### 2025-04-06 download-football-data.qmd
20250406 - career stats

First, we can compute the players' career statistics using the `calculate_stats()` function from the `nflfastR` package [@R-nflfastR].

TODO: Insert code example.

@@

Second, we can compute the players' season-by-season statistics.

@@

```{r}
#| eval: false
nfl_actualStats_seasonal_player_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  season_type = "REG")

nfl_actualStats_seasonal_team_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG")

nfl_actualStats_seasonal_player_inclPost_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  season_type = "REG+POST")

nfl_actualStats_seasonal_team_inclPost_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG+POST")
```

@@

@@

```{r}
#| eval: false
nfl_actualStats_weekly_player_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "week")

nfl_actualStats_weekly_team_raw <- calculate_stats(
  seasons = TRUE,
  summary_level = "week",
  stat_type = "team")
```

>>>>

@@

First, we can compute the players' season-by-season statistics.

@@

```{r}
#| eval: false
nfl_actualStats_seasonal_player_raw <- nflfastR::calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  season_type = "REG")

nfl_actualStats_seasonal_team_raw <- nflfastR::calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG")

nfl_actualStats_seasonal_player_inclPost_raw <- nflfastR::calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  season_type = "REG+POST")

nfl_actualStats_seasonal_team_inclPost_raw <- nflfastR::calculate_stats(
  seasons = TRUE,
  summary_level = "season",
  stat_type = "team",
  season_type = "REG+POST")
```

@@

Second, we can compute the players' career statistics using the `calculate_stats()` function from the `nflfastR` package [@R-nflfastR].

```{r}
# Compute Player Stats by Career
playerVars <- nfl_actualStats_seasonal_player %>% 
  select(games:fantasy_points_ppr) %>% 
  names()

weightedAverageVars_byGames <- c(
  "passing_epa","rushing_epa","receiving_epa",
  "target_share","air_yards_share"
)

weightedAverageVars_byAttempts <- c(
  "passing_cpoe"
)

weightedAverageVars_byTargets <- c(
  "wopr"
)

concatenateVars <- c(
  "fg_made_list","fg_missed_list","fg_blocked_list","gwfg_distance_list"
)

recomputeVars <- c(
  "pacr", # passing_yards / passing_air_yards
  "racr", # receiving_yards / receiving_air_yards
  "fg_pct", # fg_made / fg_att
  "pat_pct" # pat_att / pat_made
)

sumVars <- playerVars[playerVars %ni% c(
  weightedAverageVars_byGames, weightedAverageVars_byAttempts, weightedAverageVars_byTargets, concatenateVars, recomputeVars)]

nfl_actualStats_career_player <- nfl_actualStats_seasonal_player %>% 
  group_by(player_id) %>% 
  summarise(
    across(all_of(weightedAverageVars_byGames), ~ weighted.mean(.x, w = games, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byAttempts), ~ weighted.mean(.x, w = attempts, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byTargets), ~ weighted.mean(.x, w = targets, na.rm = TRUE)),
    across(all_of(concatenateVars), ~ paste(.x[!is.na(.x)], collapse = ";")),
    across(all_of(sumVars), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop") %>% 
  mutate(
    pacr = passing_yards / passing_air_yards,
    racr = receiving_yards / receiving_air_yards,
    fg_pct = fg_made / fg_att,
    pat_pct = pat_att / pat_made
  )

nfl_actualStats_career_player$fg_made_list[which(nfl_actualStats_career_player$fg_made_list == "")] <- NA
nfl_actualStats_career_player$fg_missed_list[which(nfl_actualStats_career_player$fg_missed_list == "")] <- NA
nfl_actualStats_career_player$fg_blocked_list[which(nfl_actualStats_career_player$fg_blocked_list == "")] <- NA
nfl_actualStats_career_player$gwfg_distance_list[which(nfl_actualStats_career_player$gwfg_distance_list == "")] <- NA

nfl_actualStats_career_player_inclPost <- nfl_actualStats_seasonal_player_inclPost %>% 
  group_by(player_id) %>% 
  summarise(
    across(all_of(weightedAverageVars_byGames), ~ weighted.mean(.x, w = games, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byAttempts), ~ weighted.mean(.x, w = attempts, na.rm = TRUE)),
    across(all_of(weightedAverageVars_byTargets), ~ weighted.mean(.x, w = targets, na.rm = TRUE)),
    across(all_of(concatenateVars), ~ paste(.x[!is.na(.x)], collapse = ";")),
    across(all_of(sumVars), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop") %>% 
  mutate(
    pacr = passing_yards / passing_air_yards,
    racr = receiving_yards / receiving_air_yards,
    fg_pct = fg_made / fg_att,
    pat_pct = pat_att / pat_made
  )

nfl_actualStats_career_player_inclPost$fg_made_list[which(nfl_actualStats_career_player_inclPost$fg_made_list == "")] <- NA
nfl_actualStats_career_player_inclPost$fg_missed_list[which(nfl_actualStats_career_player_inclPost$fg_missed_list == "")] <- NA
nfl_actualStats_career_player_inclPost$fg_blocked_list[which(nfl_actualStats_career_player_inclPost$fg_blocked_list == "")] <- NA
nfl_actualStats_career_player_inclPost$gwfg_distance_list[which(nfl_actualStats_career_player_inclPost$gwfg_distance_list == "")] <- NA
```

```{r}
nfl_actualStats_career_player %>% 
  group_by(player_id) %>% 
  filter(n() > 1) %>% 
  head()

nfl_actualStats_career_player_inclPost %>% 
  group_by(player_id) %>% 
  filter(n() > 1) %>% 
  head()
```

save(
  nfl_actualStats_career_player, nfl_actualStats_career_player_inclPost,
  file = "./data/nfl_actualStats_career.RData"
)
```

@@

```{r}
#| eval: false
nfl_actualStats_weekly_player_raw <- nflfastR::calculate_stats(
  seasons = TRUE,
  summary_level = "week")

nfl_actualStats_weekly_team_raw <- nflfastR::calculate_stats(
  seasons = TRUE,
  summary_level = "week",
  stat_type = "team")
```
